Strong coupling between scales in a multi-scalar model of urban dynamics

### 2022-09-28 Docs/Papers/Multiscale/paper/paper.tex
.

\affil*[1]{\orgdiv{LASTIG}, \orgname{Univ. Gustave Eiffel, IGN-ENSG}} %, \orgaddress{\street{73 avenue de Paris}, \city{Saint-Mand{\'e}}, \postcode{93160}, \country{France}}
\affil[2]{\orgdiv{Center for Advanced Spatial Analysis}, \orgname{University College London}} % , \orgaddress{\street{90 Tottenham Court Road}, \city{London}, \postcode{}, \country{UK}}
\affil[3]{\orgdiv{UPS CNRS 3611 ISC-PIF}, \orgname{CNRS}} % , \orgaddress{\street{Place Nationale}, \city{Paris}, \postcode{75013}, \country{France}}
\affil[4]{\orgdiv{UMR CNRS 8504 G{\'e}ographie-cit{\'e}s}, \orgname{Universit{\'e} Paris 1}} % , \orgaddress{\street{Place Nationale}, \city{Paris}, \postcode{75013}, \country{France}}

@@

Territorial dynamics, and more particularly urban dynamics, have according to \cite{pumain1997pour} an intrinsic multi-scalar nature, with successive autonomous levels of emergence from individual microscopic agents to the mesoscopic scale of the city and the macroscopic scale of the system of cities. While models at each scale with distinct ontologies are useful to answer their own questions, an explicit account of inter-scale feedbacks, both top-down and bottom-up, would allow testing policies and interventions distributed and differentiated across scales while not neglecting the interactions between scales \citep{wegener2018multi}. Indeed, the need for sustainable territorial policies would imply the construction of multi-scalar models to take simultaneously into account issues associated to each relevant scale \cite{Rozenblat2018,raimbault:halshs-02284933}.

@@

Multi-scalar models of urban dynamics are however still at their beginnings. \cite{murcio2015urban} consider population flows at different spatial ranges from the urban area to the country, but does not incorporate distinct ontologies and processes for the different scales. \cite{batty2005agents} however suggests that a similar formalism can be applied to urban processes at different scales. Multi-level statistical models capture some information at imbricated scales \cite{shu2020modelling}, although they can not be used as dynamical simulation models. Similarly, multi-level cellular automata (CA) models for urban growth include factors influencing urban expansion at multiple scales \cite{xu2019directional}. \cite{cheng2003modelling} propose a general framework for such approaches. \cite{torrens2001cellular} suggest that hybrid models coupling CA with other formalisms is a crucial development in the field. \cite{white2006modeling} introduces a CA with variable grid size to account for heterogeneities across scales. \cite{zhu2020dynamic} couple an agent-based model with a CA at multiple scales. \cite{yu2018modeling} embed a local CA into a regional intercity model and a macroscopic potential model. \cite{ford2019multi} couple at different scales an urban development model with a flooding risk model to forecast the future impact of extreme climate events on the London metropolitan region. \cite{xu2020urban} develop an agent-based model of urban expansion with both macro and micro agents. \cite{raimbault:halshs-02013006} suggests that integrating network dynamics at the link level in a macroscopic urban system models is a way to implement a multi-scale model, as done by \cite{raimbault2020hierarchy} which explores hierarchy properties of cities and networks in this context.

>>>>

\affil*[1]{\orgdiv{LASTIG}, \orgname{Univ. Gustave Eiffel, IGN-ENSG}} %, \orgaddress{\street{73 avenue de Paris}, \city{Saint-Mand{\'e}}, \postcode{93160}, \country{France}}
\affil[2]{\orgdiv{Center for Advanced Spatial Analysis}, \orgname{UCL}} % , \orgaddress{\street{90 Tottenham Court Road}, \city{London}, \postcode{}, \country{UK}}
\affil[3]{\orgdiv{UPS CNRS 3611 ISC-PIF}, \orgname{CNRS}} % , \orgaddress{\street{Place Nationale}, \city{Paris}, \postcode{75013}, \country{France}}
\affil[4]{\orgdiv{UMR CNRS 8504 G{\'e}ographie-cit{\'e}s}, \orgname{Universit{\'e} Paris 1}} % , \orgaddress{\street{Place Nationale}, \city{Paris}, \postcode{75013}, \country{France}}

@@

Territorial dynamics, and more particularly urban dynamics, have according to \cite{pumain1997pour} an intrinsic multi-scalar nature, with successive autonomous levels of emergence from individual microscopic agents to the mesoscopic scale of the city and the macroscopic scale of the system of cities. While models at each scale with distinct ontologies are useful to answer their own questions, an explicit account of inter-scale feedbacks, both top-down and bottom-up, would allow testing policies and interventions distributed and differentiated across scales while not neglecting the interactions between scales \citep{wegener2018multi}. Indeed, the need for sustainable territorial policies would imply the construction of multi-scalar models to take simultaneously into account issues associated to each relevant scale \citep{Rozenblat2018,raimbault:halshs-02284933}.

@@

Multi-scalar models of urban dynamics are however still at their beginnings. \cite{murcio2015urban} consider population flows at different spatial ranges from the urban area to the country, but does not incorporate distinct ontologies and processes for the different scales. \cite{batty2005agents} however suggests that a similar formalism can be applied to urban processes at different scales. Multi-level statistical models capture some information at imbricated scales \citep{shu2020modelling}, although they can not be used as dynamical simulation models. Similarly, multi-level cellular automata (CA) models for urban growth include factors influencing urban expansion at multiple scales \citep{xu2019directional}. \cite{cheng2003modelling} propose a general framework for such approaches. \cite{torrens2001cellular} suggest that hybrid models coupling CA with other formalisms is a crucial development in the field. \cite{white2006modeling} introduces a CA with variable grid size to account for heterogeneities across scales. \cite{zhu2020dynamic} couple an agent-based model with a CA at multiple scales. \cite{yu2018modeling} embed a local CA into a regional intercity model and a macroscopic potential model. \cite{ford2019multi} couple at different scales an urban development model with a flooding risk model to forecast the future impact of extreme climate events on the London metropolitan region. \cite{xu2020urban} develop an agent-based model of urban expansion with both macro and micro agents. \cite{raimbault:halshs-02013006} suggests that integrating network dynamics at the link level in a macroscopic urban system models is a way to implement a multi-scale model, as done by \cite{raimbault2020hierarchy} which explores hierarchy properties of cities and networks in this context.
